oolong: An R package for validating  automated content analysis tools

### 2020-07-24 paper/paper.rmd
Further update the paper

Second, results from statistical validation do not always agree with those from semantic validation. For example, a topic model with a lower perplexity does not have a better interpretability [@chang2009reading]. Of course, there are also metrics from statistical validation that are shown to be correlated with semantic validity, e.g. semantic coherence [@mimno2011optimizing]. Calculation of semantic coherence is recommended in the best practice paper by @maier2018applying. Nonetheless, conducting only statistical validation is not adequate because these three validation operations supplement each other.

>>>>

Second, results from statistical validation do not always agree with those from semantic validation. For example, a topic model with a lower perplexity does not have a better interpretability [@chang2009reading]. Of course, there are also metrics from statistical validation that are shown to be correlated with semantic validity, e.g. semantic coherence [@mimno2011optimizing]. But this correlation is also dependent on the text material. For example, @fan2019assessing show that semantic coherence is weakly correlated at best with human assessment, when the text material used for training a topic model has some frequent terms. But still, calculation of semantic coherence is recommended in the best practice paper by @maier2018applying. Nonetheless, conducting only statistical validation is not adequate because these three validation operations supplement each other.
